\GVN{}-Hoist: Hoisting Computations from Branches

### 2016-11-03 slides/gvn-hoist.tex
adding example
simplify

\begin{frame}[fragile]{CFGSimplify limits}
  \begin{columns}[T,onlytextwidth] % align columns
    \column{.4\textwidth}
    \begin{block}{\small Original program}
      \begin{lstlisting}
inv = 1/d;
if (inv >= 0) {
  tmin = min * inv;
  tmax = max * inv;
} else {
  tmin = max * inv;
  tmax = min * inv;
}
      \end{lstlisting}
    \end{block}
    \pause
    \column{.1\textwidth}
    \begin{center}
      \vspace{2cm}
      $\longrightarrow$
    \end{center}
    \column{.4\textwidth}
    \begin{block}{\small Expressions hoisted}
      \begin{lstlisting}
inv = 1/d;
x = min * inv;
y = max * inv;
if (inv >= 0) {
  tmin = x;
  tmax = y;
} else {
  tmin = y;
  tmax = x;
}
      \end{lstlisting}
    \end{block}
  \end{columns}
\end{frame}

>>>>

\begin{frame}[fragile]{CFGSimplify limits}
  \begin{columns}[T,onlytextwidth] % align columns
    \column{.4\textwidth}
    \begin{block}{\small Original program}
      \begin{lstlisting}
inv = 1/d;
if (inv >= 0) {
  ta = a * inv;
  tb = b * inv;
} else {
  ta = b * inv;
  tb = a * inv;
}
      \end{lstlisting}
    \end{block}
    \pause
    \column{.1\textwidth}
    \begin{center}
      \vspace{2cm}
      $\longrightarrow$
    \end{center}
    \column{.4\textwidth}
    \begin{block}{\small Expressions hoisted}
      \begin{lstlisting}
inv = 1/d;
x = a * inv;
y = b * inv;
if (inv >= 0) {
  ta = x;
  tb = y;
} else {
  ta = y;
  tb = x;
}
      \end{lstlisting}
    \end{block}
  \end{columns}
\end{frame}
